[Re] Spike Synchronization and Rate Modulation Differentially Involved in Motor Cortical Function

### 2017-04-23 article/VRostami_JIto_MDenker_SGruen_2016.tex
changes according to review

Figures~\ref{fig:figure2alignedPS} and ~\ref{fig:figure2alignedRS} show
the results of performing the UE analysis for PS- and RS-aligned data,
respectively. Here, the analysis parameters are set to the identical
values as reported in the original publication (bin size: 5 ms, analysis
time window size: 100 ms, time step of the sliding window: 5 ms,
significance level \(\alpha= 0.05\)). The comparison of the two figures
to the original figure shows agreement in the raster displays (panel A)
and the time-resolved, trial-averaged firing rate estimates (B).
However, although the graphs of the number of coincidences per sliding
window (panel D) and the surprise measure (panel E) are similar in their
overall general behavior, they differ in the details. Thus, indeed the
choice of the alignment influences the analysis result. In order to test
if one of the two alignments is in agreement with the original
publication, we perform a detailed visual comparison of our two figures
and the original one on the basis of the spikes marked as coincident
(panels C) and as part of a UE (panel D). We notice that when aligning
to PS (Figure~\ref{fig:figure2alignedPS}), the marked spikes do not
agree in all details with the original figure. However, in
Figure~\ref{fig:figure2alignedRS}, with trials aligned to RS, we find no
disagreements with the original figure. After this visual comparison we
check if our results are exactly identical to the original ones.
Therefore, we extract the positions of the data points representing
spikes and UEs in the original figure by reading the plotting commands
in the PDF file of the original paper, and compare them to our
reproduced results. In Figure~\ref{fig:validation_fig2} A the reproduced
spike times in Figure~\ref{fig:figure2alignedRS} A are plotted against
the extracted original spike times. The plotted data points lie on the
diagonal line, indicating that the reproduced spike times correspond to
the original ones. Figure~\ref{fig:validation_fig2} B shows the same
plot for the UEs, indicating the identity of the original and reproduced
UE timings as well. To further confirm the identity, we plot in
Figure~\ref{fig:validation_fig2} C the distributions of the differences
between the original and the reproduced timings for the spikes (black)
and the UEs (red). The differences are at most +/- 0.3 ms, which are
considerably narrower than the +/- 1 ms differences caused by the
misaligned data shown in Figure~\ref{fig:figure2alignedPS} A (see for
comparison the gray plot in Figure~\ref{fig:validation_fig2} C, which
shows the differences between the original spike times and the
misaligned spike times). The remaining minor differences of the spike
and UE times of the correctly aligned data and the original data are
only due to slight errors in the extraction of the spike times from the
original figure, which is inevitable because of a limited precision of
the plotting commands in the PDF file. Thus, we confirm that spike
timings in the correctly aligned data are identical to those in the
original data, and our implementation of the UE analysis applied to
these data reproduces exactly the same results as shown in the original
paper.

\begin{figure}[htbp]
\centering
\includegraphics{validation_results_fig2.eps}
\caption{\label{fig:validation_fig2}\textbf{A)} The scatter plot of the
reproduced spike times in Figure~\ref{fig:figure2alignedRS} A plotted
against the extracted original spike times. \textbf{B)} Same plot as in
A but for the time of occurrences of UEs. \textbf{C)} The distributions
of the differences between the original and the reproduced timings for
spikes (black) and UEs (red) in Figure~\ref{fig:figure2alignedRS}. The
distribution of the differences between the original and the reproduced
timings for spikes in Figure~\ref{fig:figure2alignedPS} is shown in
gray.}\label{fig:validationux5ffig2}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure3.eps}
\caption{\label{fig:reproducedFig4A}Reproduction of Figure 4A of the
original publication. The left part of the figure shows the UE analysis
result for the data aligned to ES1 (event code 15 in the GDF data file)
with a time before the event (pre-time) set to 699 ms. The right part of
the figure shows the analysis of the same data aligned to RS and with a
pre-time of 99 ms. The left and right parts of the figure show 96 and
128 trials, respectively.}\label{fig:reproducedFig4A}
\end{figure}

>>>>

Figures~\ref{fig:figure2alignedPS} and ~\ref{fig:figure2alignedRS} show
the results of performing the UE analysis for PS- and RS-aligned data,
respectively. Here, the analysis parameters are set to the identical
values as reported in the original publication (bin size: 5 ms, analysis
time window size: 100 ms, time step of the sliding window: 5 ms,
significance level \(\alpha= 0.05\)). The comparison of the two figures
to the original figure shows agreement in the raster displays (panel A)
and the time-resolved, trial-averaged firing rate estimates (B).
However, although the graphs of the number of coincidences per sliding
window (panel D) and the surprise measure (panel E) are similar in their
overall general behavior, they differ in the details. Thus, indeed the
choice of the alignment influences the analysis result. In order to test
if one of the two alignments is in agreement with the original
publication, we perform a detailed visual comparison of our two figures
and the original one on the basis of the spikes marked as coincident
(panels C) and as part of a UE (panel D). We notice that when aligning
to PS (Figure~\ref{fig:figure2alignedPS}), the marked spikes do not
agree in all details with the original figure. However, in
Figure~\ref{fig:figure2alignedRS}, with trials aligned to RS, we find no
disagreements with the original figure. After this visual comparison we
check if our results are exactly identical to the original ones.
Therefore, we extract the positions of the data points representing
spikes and UEs in the original figure by reading the plotting commands
in the PDF file of the original paper, and compare them to our
reproduced results. In Figure~\ref{fig:validation_fig2} A the reproduced
spike times in Figure~\ref{fig:figure2alignedRS} A are plotted against
the extracted original spike times. The plotted data points lie on the
diagonal line, indicating that the reproduced spike times correspond to
the original ones. Figure~\ref{fig:validation_fig2} B shows the same
plot for the UEs, indicating the identity of the original and reproduced
UE timings as well. To further confirm the identity, we plot the
distributions of the differences between the original and the reproduced
timings for the spikes (Figure~\ref{fig:validation_fig2} C; black) and
the UEs (Figure~\ref{fig:validation_fig2} D). The differences are at
most +/- 0.3 ms, which are considerably narrower than the +/- 1 ms
differences caused by the misaligned data shown in
Figure~\ref{fig:figure2alignedPS} A (see for comparison the gray plot in
Figure~\ref{fig:validation_fig2} C, which shows the differences between
the original spike times and the misaligned spike times). The remaining
minor differences of the spike and UE times of the correctly aligned
data and the original data are only due to slight errors in the
extraction of the spike times from the original figure, which is
inevitable because of a limited precision of the plotting commands in
the PDF file. Thus, we confirm that spike timings in the correctly
aligned data are identical to those in the original data, and our
implementation of the UE analysis applied to these data reproduces
exactly the same results as shown in the original paper.

\begin{figure}[htbp]
\centering
\includegraphics{validation_results_fig2.eps}
\caption{\label{fig:validation_fig2}\textbf{A)} The scatter plot of the
reproduced spike times in Figure~\ref{fig:figure2alignedRS} A plotted
against the extracted original spike times. \textbf{B)} Same plot as in
A but for the time of occurrences of UEs. \textbf{C)} The distributions
of the differences between the original and the reproduced timings for
spikes in Figure ~\ref{fig:figure2alignedRS} and
Figure~\ref{fig:figure2alignedPS} are shown in black and gray,
respectively. \textbf{D)} Same plot as in C but for UEs in Figure
~\ref{fig:figure2alignedRS}.}\label{fig:validationux5ffig2}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure6.eps}
\caption{\label{fig:reproducedFig4A}Reproduction of Figure 4A of the
original publication. The left part of the figure shows the UE analysis
result for the data aligned to ES1 (event code 15 in the GDF data file)
with a time before the event (pre-time) set to 699 ms. The right part of
the figure shows the analysis of the same data aligned to RS and with a
pre-time of 99 ms. The left and right parts of the figure show 96 and
128 trials, respectively.}\label{fig:reproducedFig4A}
\end{figure}
